Project setup

### 2022-02-11 analysis/setup.Rmd
update Neale directory with newly downloaded files

```{r, engine = 'bash', eval = FALSE}
project_dir=/data/sgg2/jenny/projects/proxyMR
mkdir $project_dir/data/raw
mkdir $project_dir/data/processed
mkdir $project_dir/docs/assets
mkdir $project_dir/docs/generated_reports
mkdir $project_dir/analysis/data_setup
mkdir $project_dir/analysis/data_setup/IV_lists
mkdir $project_dir/analysis/data_setup/IV_info
mkdir $project_dir/analysis/data_setup/sex_heterogeneity
mkdir $project_dir/analysis/traitMR
mkdir $project_dir/analysis/traitMR/IVs
mkdir $project_dir/analysis/traitMR/IVs/Neale
mkdir $project_dir/analysis/traitMR/household_MR
mkdir $project_dir/analysis/traitMR/household_GWAS
mkdir $project_dir/analysis/traitMR/standard_GWAS
mkdir $project_dir/analysis/traitMR/standard_MR
mkdir $project_dir/analysis/traitMR/trait_info
mkdir $project_dir/analysis/traitMR/pheno_files
mkdir $project_dir/analysis/traitMR/pheno_files/phesant
mkdir $project_dir/analysis/traitMR/pheno_files/raw_change
mkdir $project_dir/output/figures
mkdir $project_dir/output/tables
mkdir $project_dir/output/figures/traitMR
mkdir $project_dir/output/tables/traitMR

>>>>

```{r, engine = 'bash', eval = FALSE}
project_dir=/data/sgg2/jenny/projects/proxyMR
mkdir $project_dir/data/raw
mkdir $project_dir/data/processed
mkdir $project_dir/docs/assets
mkdir $project_dir/docs/generated_reports
mkdir $project_dir/analysis/data_setup
mkdir $project_dir/analysis/data_setup/IV_lists
mkdir $project_dir/analysis/data_setup/IV_info
mkdir $project_dir/analysis/data_setup/sex_heterogeneity
mkdir $project_dir/analysis/traitMR
mkdir $project_dir/analysis/traitMR/IVs
mkdir $project_dir/analysis/traitMR/IVs/Neale
mkdir $project_dir/analysis/traitMR/household_MR
mkdir $project_dir/analysis/traitMR/household_GWAS
mkdir $project_dir/analysis/traitMR/standard_GWAS
mkdir $project_dir/analysis/traitMR/household_GWAS_rev_filter
mkdir $project_dir/analysis/traitMR/standard_GWAS_rev_filter
mkdir $project_dir/analysis/traitMR/standard_MR
mkdir $project_dir/analysis/traitMR/trait_info
mkdir $project_dir/analysis/traitMR/pheno_files
mkdir $project_dir/analysis/traitMR/pheno_files/phesant
mkdir $project_dir/analysis/traitMR/pheno_files/raw_change
mkdir $project_dir/output/figures
mkdir $project_dir/output/tables
mkdir $project_dir/output/figures/traitMR
mkdir $project_dir/output/tables/traitMR
